Sea: A lightweight data-placement library for Big Data scientific computing

### 2022-03-29 paper/sea-comp/paper.tex
Minor fixes

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Hayot-Sasson\MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for
Computer Society Journals} \IEEEtitleabstractindextext{%
\begin{abstract}
    The recent influx of scientific data has lead to scientific computing
transitioning from compute intensive to data intensive. Whereas many Big Data
Frameworks exist that minimize the cost of data transfers, few scientific
applications adopt data-placement strategies as the efforts required to update
the existing applications is significant.

We developed Sea as a means to enable data-placement strategies for scientific
applications executing on HPC clusters without the need to reinstrument
workflows. Sea leverages GNU C library interception to intercept POSIX-compliant
file system calls made by the applications. We designed a performance model and
evaluated the performance of Sea on a synthetic data-intensive application
processing a representative neuroimaging dataset (the Big Brain). Our results
demonstrate that Sea significantly improves performance, up to a factor of
3$\times$.

@@

Data-placement strategies can complement existing solutions by facilitating the
transfer and processing of large datasets across different infrastructures, and
placing the different file formats at the preferred storage layer to maximize
efficiency. However, adapting existing scientific applications to Big Data
frameworks requires considerable effort, necessitating the rewrite of many well
established applications. Furthermore, as noted in \cite{mehta2017comparative},
Big Data frameworks are not easy to use for the processing of certain scientific
data, such as imaging data, due to the level of expertise required to rewrite
reference implementations using the frameworks.

@@

We developed Sea, a user-space data-placement library, that provides efficient
data placement without reinstrumentation of the underlying application. Given a
predefined storage hierarchy, Sea can prefetch, cache, flush and evict data to
and from a permanent storage location. To assist in providing a
frame-of-reference for Sea's performance on HPC systems, we designed a
performance model. We then evaluated Sea's performance on a synthetic Big Data
application running on a representative neuroimaging dataset, comparing its
performance with the bounds delineated by the model.

>>>>

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Hayot-Sasson\MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for
Computer Society Journals} \IEEEtitleabstractindextext{%
\begin{abstract}
    The recent influx of scientific data has lead to scientific computing
transitioning from compute intensive to data intensive. Whereas many Big Data
Frameworks exist that minimize the cost of data transfers, few scientific
applications adopt data-placement strategies as the efforts required to update
the existing applications is significant.
We developed Sea as a means to enable data-placement strategies for scientific
applications executing on HPC clusters without the need to reinstrument
workflows. Sea leverages GNU C library interception to intercept POSIX-compliant
file system calls made by the applications. We designed a performance model and
evaluated the performance of Sea on a synthetic data-intensive application
processing a representative neuroimaging dataset (the Big Brain). Our results
demonstrate that Sea significantly improves performance, up to a factor of
3$\times$.

@@

Data-placement strategies can complement existing solutions by facilitating
the transfer and processing of large datasets across different
infrastructures, and placing the different file formats at the preferred
storage layer to maximize efficiency. However, adapting existing scientific
applications to Big Data frameworks requires considerable effort,
necessitating the rewrite of many well-established applications.
Furthermore, as noted in \cite{mehta2017comparative}, Big Data frameworks
are not easy to use for the processing of certain scientific data, such as
imaging data, due to the level of expertise required to rewrite reference
implementations using the frameworks.

@@

We developed Sea, a user-space data-placement library that provides efficient
data placement without reinstrumentation of the underlying application. Given a
predefined storage hierarchy, Sea can prefetch, cache, flush, and evict data to
and from a permanent storage location. To provide a
frame-of-reference for Sea's performance on HPC systems, we designed a
performance model. We then evaluated Sea's performance on a synthetic Big Data
application running on a representative neuroimaging dataset, comparing its
performance with the bounds delineated by the model.
